An event-sourced and decentralized database with IPLD and materialized views

### 2019-09-27 draft.tex
edit fixes
Signed-off-by: andrew <andrew@textile.io>

In multi-writer systems, conflicts arise as disparate peers end up producing conflicting state changes, or changes that end up out of sync. In order to proceed, there must be some way to deal with these conflicts. In some cases (e.g, \texttt{ipfs-log} \cite{markroberthendersonOrbitDBFieldManual2019}), a Merkle-Clock can be used to induce ordering. This approach cannot achieve a total order of events without implementing a data-layer conflict resolution strategy and therefor still requires, data-layer conflict resolution \cite{sanjuanMerkleCRDTs2019}:

@@

Therefore, solutions such as \texttt{ipfs-log} include a built-in CRDT to manage conflicts not resolved by the Merkle-Clock. This approach works for many cases, but the use of a deterministic merge strategy can be insufficient in cases where complicated data structures or long chains of missed events need to be reconciled. A git merge highlights one such example, in which a predetermined merge strategy can be used, but is not often the best choice in practice. Furthermore, a multi-writer log using a linked data format (e.g., a Merkle-Dag) in imperfect networking or storage environments can lead to suboptimal states where it may exceedingly costly (networking, storage, and computation) to regain consistency.

>>>>

In multi-writer systems, conflicts arise as disparate peers end up producing disconnected state changes, or changes that end up out of sync. In order to proceed, there must be some way to deal with these conflicts. In some cases (e.g, \texttt{ipfs-log} \cite{markroberthendersonOrbitDBFieldManual2019}), a Merkle-Clock can be used to induce ordering. This approach cannot achieve a total order of events without implementing a data-layer conflict resolution strategy \cite{sanjuanMerkleCRDTs2019}:

@@

Therefore, solutions such as \texttt{ipfs-log} include a built-in CRDT to manage conflicts not resolved by the Merkle-Clock. This approach works for many cases, but the use of a deterministic resolution strategy can be insufficient in cases where complicated data structures or long chains of missed events need to be reconciled. A git merge highlights one such example, in which a predetermined merge strategy can be used, but is not often the best choice in practice. Furthermore, a multi-writer log using a linked data format (e.g., a Merkle-Dag) in imperfect networking or storage environments can lead to suboptimal states where it may exceedingly costly (networking, storage, and computation) to regain consistency.
